\documentclass[10.5pt]{article}
\usepackage[margin=2.5em]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{titlesec}
\titlespacing{\section}{0pt}{\parskip}{-\parskip}
\linespread{0.8}

\newenvironment{sect}[1][]
{ \section*{\textsc{#1}} \noindent \begin{tabular}{p{5.3em} p{48em}} }
{ \end{tabular} }

\titleformat{\section}
  {\normalfont\fontsize{12}{15}\bfseries}{\thesection}{1em}{}

\begin{document}

\pagenumbering{gobble}

\centerline{\LARGE \textbf{\textsc{Patrik Ackland}}}

\begin{center}
  \url{http://www.csc.kth.se/~packland} \\
  \vspace{0.3em}
  \begin{tabular}{l r}
    packland@cs.uw.edu&(206) 890-8507
  \end{tabular} \\
  \vspace{0.3em}
  \textbf{Graduating in June 2017. Looking for a summer internship.\\I have a J1 visa sponsored by the University of Washington which allows me to work in the US for nine months}
\end{center}

\begin{sect}[Education]
  2015--(2016)&\textbf{Departmental exchange, Computer Science, \textit{University of Washington\hfill Seattle, USA}}\\
  &-- Highly competitive selection process. Only one student from my university admitted every year.\\
  &-- Selection based on GPA.\\ \\

  2012--(2017)&\textbf{Combined BS/MS, Computer Science, \textit{KTH Royal Institute of Technology\hfill Stockholm, Sweden}}\\
  &-- Courses in algorithms, complexity, programming paradigms and compiler construction. \\
  &-- GPA: 4.8/5.0.
\end{sect}

\begin{sect}[Experience]
  2015--2015&\textbf{Software Engineering Intern, \textit{Scania R\&D\hfill Södertälje, Sweden}}\\
  &-- Continued developing project from the previous year.\\
  &-- Implemented requests from teams within the company.\\
  &-- Added several new features including digital envelope cryptography using open-ssl.\\
  &Skills: C, C++, Cryptography, MATLAB. \\ \\
  2013--2015&\textbf{Teaching Assistant, \textit{KTH Royal Institute of Technology\hfill Stockholm, Sweden}}\\
  &-- Teaching programming and algorithms to 15 computer-science students.\\
  &-- Grading weekly assignments and supervising month-long project at the end of the course. \\
  &Skills: Java, Go, Theoretical computer science. \\ \\

  2014--2014&\textbf{Software Engineering Intern, \textit{Scania R\&D\hfill Södertälje, Sweden}}\\
  &-- Developed software for logging road and vehicle data in trucks.\\
  &-- The software replaced commercial software saving thousands of dollars.\\
  &-- Automated build process and optimized code for existing project. \\
  &Skills: C, C\#, Agile development. \\
\end{sect}

\begin{sect}[Projects]
  2015&\textbf{Compiler in Scala, project course\hfill \textit{Scala}} \\
  &-- Compiles a subset of Scala to JVM bytecode.\\
  &-- Handwritten lexer, parser, name analyzer and type checker.\\
  &-- Supports Java-like generics through type erasure.\\
  &-- Received an A, the highest grade.\\ \\

  2015--&\textbf{Chromium, open source web browser\hfill \textit{C++}} \\
  &-- Currently working on good-first-bugs. \\
  &-- Looking to work on more complex issues as I get more experience.\\ \\

  2015&\textbf{Picture-of-pictures, personal project\hfill \textit{Ruby, JavaScript}} \\
  &-- Replaces each pixel in an image with an image whose dominant color is closest to the color of the pixel.\\
  &-- Choosing better data structures reduced running time by 90\%. \\ \\

  2015&\textbf{Distributed data mining, research project\hfill \textit{C++}} \\
  &-- Resulted in bachelor thesis.\\
  &-- Investigated how a specific graph mining algorithm performed on different graph models.\\
  &-- The thesis received an A, the highest grade. \\ \\
  &More projects can be found at \url{http://www.csc.kth.se/~packland} \\
\end{sect}

\begin{sect}[Programming]
  Main:&\textbf{Java (6 years)}, \textbf{Android (2 years)}, \textbf{C++ (2 years)} \\
  Other:&C\#, JavaScript, Scala, Ruby, Go
\end{sect}
\vspace{1em}
\begin{sect}[Leadership experience]
  2014--2014&\textbf{Head of Sponsor, International Reception\hfill \textit{KTH Student Union}} \\
  &-- Spent six months together with 13 other students planning the international reception.\\
  &-- Welcomed over 2000 students during four arrival days and planned a month of activities. \\ \\

  2013--2014&\textbf{President of the Education Committee\hfill \textit{KTH, Computer Science Chapter}} \\
  &-- Nominated by my predecessor because of my involvement the previous year.\\
  &-- Meetings with students and faculty to discuss courses and the computer science department.
\end{sect}

\begin{sect}[Awards]
  2015&\textbf{Henrik Göransson Sandviken Scholarship} \\
  &-- Awarded scholarship for academic achievements at KTH Royal Institute of Technology.\\
  &-- Selection based on GPA. Awarded to 90 students in total from all majors at the university.
\end{sect}

\begin{sect}[Other]
  Clubs:&UW photography club, education committee, business-relations group, international reception. \\
  Interests:&photography, guitar.
\end{sect}
\end{document}
